Measuring individual differences in the understanding of gaze cues

### 2022-04-28 paper/manuscript.Rmd
new fig4, fix ccAge calculation error, incorporate some of M feedback

@@

## Implementation [m: das vll zuerst - vor der Beschreibung der versionen]
Our balloon finding task is presented as an interactive web-app. The task is portable across devices and web browsers and does not require any installation. An advantage of online testing is that our testing procedure is standardized across participants. By using pre-recorded study instructions, no interaction with the experimenter is necessary during the study. The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.

The web-app was programmed in `JavaScript` (ECMAScript 2015, i.e., ES6), `HTML5`, `CSS` and `PHP`. For stimulus presentation, a scalable vector graphic (SVG) composition was parsed. This way, the composition scales according to the user's view port without loss of quality, while keeping the aspect ratio and relative object positions constant. Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually. This is needed for precisely calculating exact pupil and target locations and sizes. Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene. The web-app generates two file types: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording. These files can either be sent to a server or downloaded to the local device.

# Individual differences
Our first aim was to assess whether our balloon finding task induces interindividual variation in a child and adult sample. Furthermore, we were interested in how the data collection mode influences responses.

@@

## Results
(ref:figlab2) **Measuring interindividual variation**. 
(A) Developmental trajectory in continuous hedge version. Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center. 
(B) Internal consistency (odd-even split) in hedge child sample. (C) Internal consistency in hedge adult sample. (D) Test-retest reliability in hedge child sample. (E) Test-retest reliability in hedge adult sample.
(F) Developmental trajectory in discrete box version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target. Dotted black line shows level of performance expected by chance (for child sample 20%, i.e., 1 out of 5 boxes; for adult sample 12.5%, i.e., 1 out of 8 boxes).
(G) Internal consistency (odd-even split) in box child sample. (H) Internal consistency in box adult sample. (I) Test-retest reliability in box child sample. (J) Test-retest reliability in box adult sample.
Regression lines with 95% CI show product-moment-correlations with *Pearson*'s correlation coefficient *r*. [m: die regressions linie ist ein smoothed mean based on liner model - guck einfach mal ?geom_smooth] 
Large points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). 
Small points show the mean performance for each subject. Shape of data points represents data collection mode: opaque circles for in-person supervised data collection, translucent diamonds  for remote unsupervised data collection. Color of data points denotes age group.

@@

We found a strong developmental effect: with increasing age, participants got more and more accurate in locating the target. In the hedge version, children's click imprecision decreased with age, while, in the box version the proportion of correct responses increased (see Figure 2 A and F [m: siehe oben wie man auf die figures verweist]). Most participants in the box version performed above chance level. By the end of their sixth year of life, children came close to the adult's proficiency level. Most impoertantly, however, we found subtantial interindividual variation across study versions and age groups. For example, some three-year-olds were more precise in their responses than some five-year-olds [m: jetzt noch was zu den erwachsenene - sagen ,dass da auch variation ist; weniger als bei den kindern, but still].

As Figure 2 A and F show, our remotely collected child data resembled the data from the kindergarten sample. 
We found evidence that responses of children participating remotely were slightly more precise. This difference was mainly driven by the younger participants and especially prominent in the box version of the task. It is conceivable that caregivers were especially prone to influence the behavior of younger children. In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.[^fn1]

@@

Our GLMM analysis corroborated the visual inspection of the data: in the hedge version, we the estimates for age of ($\beta$ = `r fixef(mAgeHedge)["age", "Estimate"]`; 95% CI [`r fixef(mAgeHedge)["age", "Q2.5"]`; `r fixef(mAgeHedge)["age", "Q97.5"]`]) and data collection mode `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q97.5"]`]) were reliably different from zero [m: so würde ich alle estiamtes berichten. also sagen ob positive oder negative und ob veschieden von 0 oder nicht]. 
In the box version, the estimate of age was `r fixef(mAgeBox)["age", "Estimate"]` (95% CI [`r fixef(mAgeBox)["age", "Q2.5"]`; `r fixef(mAgeBox)["age", "Q97.5"]`]) and the estimate of data collection mode was `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q97.5"]`]). Note that the effect of data collection appears to be present, but confidence intervals are wide [m: das präziser - positive effect, but nor reliably different from 0 oder so].

## Discussion
Our task induced interintidivudal variation in both adults and children. With increasing age, participants got more and more precise in locating the target. Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample. This illustrates the flexibility of the task.

@@

As a next step, we aimed at investigating whether the variation that we captured with our balloon finding task is reliable. We assessed internal consistency (split-half reliability) and test-retest reliability. Data collection and analysis were pre-registered (can be found here: )https://osf.io/xqm73 (child sample),  https://osf.io/nu62m (adult sample)). Participants were equally distributed across the two study versions. The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology. Data was collected between July 2021 and April 2022.

@@

Second, we assessed the test-retest reliability. We calculated performance scores (depending on study version as described above) for each participant in each test session and correlated them using *Pearson* correlation coefficients. Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach [m: hier noch das paper zitieren]. We fit trial by trial data with a fixed effect of age, a random intercept for each subject and a random slope for test day (model notation in `R: performance ~ age (0 + reliday | subjID)`). For the hedge version, performance was modeled by a lognormal distribution, while the model for the box version used a Bernoulli distribution with a logit link function. The model computes a correlation between the participant specific estimates for each test day. This can be interpreted as the test-retest reliability. By using this approach, we do not need to compromise on data aggregation and, therefore, loss of information. Most importantly, the model allows us to get an age-independent estimate for reliability. This rules out the possibility that a high correlation between test days arises from domain general cognitive development instead of study-specific inter-individual differences [m: das noch bisschen konkreter machen. also wann würden wir eine hohe korrelation sehen und wie kümmert sich das model da drum; also maturation ist sehr loaded - einfach domain general cognitive development].

@@

We found that our balloon finding task induced systematic variation: splithalf and test-retest reliability was high for most samples. For the internal consistency, we show traditional odd-even splits on our data and the corresponding *Pearson* correlation coefficients in Figure 2 B, C, G and H. Figure 3 compares splithalf reliability coefficients by splitting and stratification method [@pronk2021methods].
In the hedge version, the splithalf reliability coefficients ranged from `r min(splithalf$coefficient[splithalf$studyversion == "hedge"])` to `r max(splithalf$coefficient[splithalf$studyversion == "hedge"])`. In the box version, splithalf reliability coefficients ranged from `r min(splithalf$coefficient[splithalf$studyversion == "box"])` to `r max(splithalf$coefficient[splithalf$studyversion == "box"])`. 
Similarly to the results of @pronk2021methods, we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients. In the majority of cases, stratifying by target position lead to similar or even higher estimates compared to no stratification. As might be expected, we found higher coefficients for the samples with higher variation, i.e., for our continuous hedge version of the task.

@@

```{r retestmodels}
mRetestHedge <- readRDS(file = "../saves/mRetestHedge.rds") 
mRetestBox <- readRDS(file = "../saves/mRetestBox.rds") 
```
For the test-retest reliability, we show the association between raw performance scores of the two test days and corresponding *Pearson* correlation coefficients in Figure 2 D, E, I and J.[^fn2]

@@

## Discussion
Our results indicated that the measured variation was systematic. As could be expected, the continuous measure of the hedge version yielded higher reliability estimates than the discrete box version. For children, the model based reliability estimates showed that the task did capture individual differences even when correcting for age. This corroborates what we already see in Figure 2: there was a clear overlap between age groups, indicating that age is predictive of performance for the mean, but is not the main source of individual differences.

@@

## Analysis
To estimate the effects of social surrounding on gaze cue understanding, we fit GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (in months, z-transformed), data collection mode (reference category: in-person supervised) and study version (reference category: hedge version). The models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants. Therefore, our null model closely resembled the structure from our first analysis (see Analysis section of *Does the balloon finding task induce variation?*; here: `performance ~ age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition)`). 
In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome. For the target position, we categorized two adjacent bins as one imaginary box. To measure participants' performance, we created imaginary box boundaries around the target's landing position and examined whether the participant's click response fell into this imaginary box. Across the two study versions, we could consequently model the participant's correct response (0/1) using a `Bernoulli` distribution with a logit link function.
For model comparisons, we ran separate models, each with one of the following predictors as a fixed effects added to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subject entered childcare. 
In addition, we calculated three index scores. First, we calculated a sibling variety score according to @peterson2000kindred. Second, we implemented the modified version of @cassidy2005theory (for more details, see Supplements). Third, based on our own data exploration, we calculated the amount of peer exposure determined as the number of siblings and the average hours spent in childcare (both z-transformed). 
We compared the models using WAIC (widely applicable information criterion) scores and weights [m: cite MCElreath dafür]. As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit. WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.

@@

The model including our peer exposure index, as defined as the number of other children in the household and average hours spent in childcare, showed the best out-of-sample predictive accuracy. Note that we did not find a great difference in WAIC scores between the compared models (see Supplements for WAIC scores and weights). The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95% CIs included zero. For example, for our winning model, we found a peer exposure estimate of [m: hier bitte auch immer beta = notation machen]
`r fixef(mExtvaliPE)["pe", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["pe", "Q2.5"]`; `r fixef(mExtvaliPE)["pe", "Q97.5"]`]),
with the estimates of age being `r fixef(mExtvaliPE)["age", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["age", "Q2.5"]`; `r fixef(mExtvaliPE)["age", "Q97.5"]`]), data collection mode being `r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Q97.5"]`]), and study version `r fixef(mExtvaliPE)["studyversionbox", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["studyversionbox", "Q2.5"]`; `r fixef(mExtvaliPE)["studyversionbox", "Q97.5"]`]). Nevertheless, a general pattern emerges: exposure to a more vairable social environment positively influenced children's gaze cue understanding. The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to follow [m: na na .. ich dachte wir messen gaze cue *understanding*] the agent's gaze. The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the better performance in the task.

[m: figure 4 gefällt mir noch nciht so gut - vll kannst du noch point estimates und Cis mit reinmachen. so wie bei den gafo-clt merge plots. Die sind hier: https://github.com/ccp-eva/vocab/blob/main/analysis/clt_gafo_merge.Rmd, Zeile 114]

@@

```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
knitr::include_graphics("../figures/extvali-posteriorsample.png")
```

>>>>

## Implementation
Our balloon finding task is presented as an interactive web app. The task is portable across devices and web browsers and does not require any installation. An advantage of online testing is that our testing procedure is standardized across participants. By using pre-recorded study instructions, no interaction with the experimenter is necessary during the study. The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.

The web app was programmed in `JavaScript`, `HTML5`, `CSS` and `PHP`. For stimulus presentation, a scalable vector graphic (SVG) composition was parsed. This way, the composition scales according to the user's view port without loss of quality, while keeping the aspect ratio and relative object positions constant. Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually. This is needed for precisely calculating exact pupil and target locations and sizes. Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene. The web app generates two file types: (1) a text file (.json) containing meta-data, trial specifications and participants' click responses, and (2) a video file (.webm) of the participant's webcam recording. These files can either be sent to a server or downloaded to the local device.

@@

# Individual differences
Our first aim was to assess whether our balloon finding task induces inter-individual variation in a child and adult sample. Furthermore, we were interested in how the data collection mode influences responses.

@@

## Results
(ref:figlab2) **Measuring inter-individual variation**. 
(A) Developmental trajectory in continuous hedge version. Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center. 
(B) Internal consistency (odd-even split) in hedge child sample. (C) Internal consistency in hedge adult sample. (D) Test-retest reliability in hedge child sample. (E) Test-retest reliability in hedge adult sample.
(F) Developmental trajectory in discrete box version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target. Dotted black line shows level of performance expected by chance (for child sample 20%, i.e., 1 out of 5 boxes; for adult sample 12.5%, i.e., 1 out of 8 boxes).
(G) Internal consistency (odd-even split) in box child sample. (H) Internal consistency in box adult sample. (I) Test-retest reliability in box child sample. (J) Test-retest reliability in box adult sample.
Regression lines with 95% CI as smoothed mean based on a linear model, with *Pearson*'s correlation coefficient *r*.
Large points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). 
Small points show the mean performance for each subject. Shape of data points represents data collection mode: opaque circles for in-person supervised data collection, translucent diamonds  for remote unsupervised data collection. Color of data points denotes age group.

@@

We found a strong developmental effect: with increasing age, participants got more and more accurate in locating the target. In the hedge version, children's click imprecision decreased with age, while, in the box version the proportion of correct responses increased (see Figure \@ref(fig:fig2)A and F). Most participants in the box version performed above chance level. By the end of their sixth year of life, children came close to the adult's proficiency level. Most importantly, however, we found substantial inter-individual variation across study versions and age groups. For example, some three-year-olds were more precise in their responses than some five-year-olds. Even though variation is smaller, we even find inter-individual differences in the adult sample.

As Figure \@ref(fig:fig2)A and F show, our remotely collected child data resembled the data from the kindergarten sample. 
We found evidence that responses of children participating remotely were slightly more precise. This difference was mainly driven by the younger participants and especially prominent in the box version of the task. It is conceivable that caregivers were especially prone to influence the behavior of younger children. In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.[^fn1]

@@

Our GLMM analysis corroborated the visual inspection of the data: in the hedge version, the estimates for age ($\beta$ = `r fixef(mAgeHedge)["age", "Estimate"]`; 95% CI [`r fixef(mAgeHedge)["age", "Q2.5"]`; `r fixef(mAgeHedge)["age", "Q97.5"]`]) and data collection mode `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeHedge)["datacollectionremoteMunsupervised", "Q97.5"]`]) were negative and reliably different from zero.
In the box version, the estimate of age ($\beta$ =`r fixef(mAgeBox)["age", "Estimate"]` (95% CI [`r fixef(mAgeBox)["age", "Q2.5"]`; `r fixef(mAgeBox)["age", "Q97.5"]`]) and the estimate of data collection mode  ($\beta$ = `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mAgeBox)["datacollectionremoteMunsupervised", "Q97.5"]`]) were positive and reliably different from zero. Note that even though confidence intervals from the data collection estimates were wide, the effect was positive and reliably different from zero in a way that our remote sample performed more accurately than our in-person sample.

## Discussion
Our task induced inter-individual variation in both adults and children. With increasing age, participants got more and more precise in locating the target. Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample. This illustrates the flexibility of the task.

@@

As a next step, we aimed at investigating whether the variation that we captured with our balloon finding task is reliable. We assessed internal consistency (split-half reliability) and test-retest reliability. Data collection and analysis were pre-registered (can be found here: https://osf.io/xqm73 for child sample, and https://osf.io/nu62m adult sample). Participants were equally distributed across the two study versions. The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology. Data was collected between July 2021 and April 2022.

@@

Second, we assessed the test-retest reliability. We calculated performance scores (depending on study version as described above) for each participant in each test session and correlated them using *Pearson* correlation coefficients. Furthermore, for our child sample we report an age-corrected correlation between the two test days using a GLMM based approach [@rouder2019psychometrics]. We fit trial by trial data with a fixed effect of age, a random intercept for each subject and a random slope for test day (model notation in `R: performance ~ age (0 + reliday | subjID)`). For the hedge version, performance was modeled by a lognormal distribution, while the model for the box version used a Bernoulli distribution with a logit link function. The model computes a correlation between the participant specific estimates for each test day. This can be interpreted as the test-retest reliability. By using this approach, we do not need to compromise on data aggregation and, therefore, loss of information. Most importantly, the model allows us to get an age-independent estimate for reliability. This rules out the possibility that a high correlation between test days arises from domain general cognitive development instead of study-specific inter-individual differences [m: das noch bisschen konkreter machen. also wann würden wir eine hohe korrelation sehen und wie kümmert sich das model da drum].

@@

We found that our balloon finding task induced systematic variation: splithalf and test-retest reliability was high for most samples. For the internal consistency, we show traditional odd-even splits on our data and the corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)B, C, G and H. Figure \@ref(fig:fig3) compares splithalf reliability coefficients by splitting and stratification method [@pronk2021methods].
In the hedge version, the splithalf reliability coefficients ranged from `r min(splithalf$coefficient[splithalf$studyversion == "hedge"])` to `r max(splithalf$coefficient[splithalf$studyversion == "hedge"])`. In the box version, splithalf reliability coefficients ranged from `r min(splithalf$coefficient[splithalf$studyversion == "box"])` to `r max(splithalf$coefficient[splithalf$studyversion == "box"])`. 
Similarly to the results of @pronk2021methods, we found that more robust splitting methods that are less prone to task design or time confounds yielded higher reliability coefficients. In the majority of cases, stratifying by target position lead to similar or even higher estimates compared to no stratification. As might be expected, we found higher coefficients for the samples with higher variation, i.e., for our continuous hedge version of the task.

@@

```{r retestmodels}
mRetestHedge <- readRDS(file = "../saves/mRetestHedge.rds") 
mRetestBox <- readRDS(file = "../saves/mRetestBox.rds") 
```
For the test-retest reliability, we show the association between raw performance scores of the two test days and corresponding *Pearson* correlation coefficients in Figure \@ref(fig:fig2)D, E, I and J.[^fn2]

@@

## Discussion
Our results indicated that the measured variation was systematic. As could be expected, the continuous measure of the hedge version yielded higher reliability estimates than the discrete box version. For children, the model based reliability estimates showed that the task did capture individual differences even when correcting for age. This corroborates what we already see in Figure \@ref(fig:fig2): there was a clear overlap between age groups, indicating that age is predictive of performance for the mean, but is not the main source of individual differences.

@@

## Analysis
To estimate the effects of social surrounding on gaze cue understanding, we fit GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (in months, z-transformed), data collection mode (reference category: in-person supervised) and study version (reference category: hedge version). The models included random intercepts for each participant and each target position, and a random slope for symmetric target position within participants. Therefore, our null model closely resembled the structure from our first analysis (see Analysis section of *Does the balloon finding task induce variation?*; here: `performance ~ age + datacollection + studyversion + (symmetricPosition | subjID) + (1 | targetPosition)`). 
In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome. For the target position, we categorized two adjacent bins as one imaginary box. To measure participants' performance, we created imaginary box boundaries around the target's landing position and examined whether the participant's click response fell into this imaginary box. Across the two study versions, we could consequently model the participant's correct response (0/1) using a `Bernoulli` distribution with a logit link function.
For model comparisons, we ran separate models, each with one of the following predictors as a fixed effects added to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subject entered childcare. 
In addition, we calculated three index scores. First, we calculated a sibling variety score according to @peterson2000kindred. Second, we implemented the modified version of @cassidy2005theory (for more details, see Supplements). Third, based on our own data exploration, we calculated the amount of peer exposure determined as the number of siblings and the average hours spent in childcare (both z-transformed). 
We compared the models using WAIC (widely applicable information criterion) scores and weights [@mcelreath2020statistical]. As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit. WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.

@@

The model including our peer exposure index, as defined as the number of other children in the household and average hours spent in childcare, showed the best out-of-sample predictive accuracy. Note that we did not find a great difference in WAIC scores between the compared models (see Supplements for WAIC scores and weights). The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95% CIs included zero. For example, for our winning model, we found a peer exposure estimate of $\beta$ =
`r fixef(mExtvaliPE)["pe", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["pe", "Q2.5"]`; `r fixef(mExtvaliPE)["pe", "Q97.5"]`]),
with the estimates of age being $\beta$ =`r fixef(mExtvaliPE)["age", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["age", "Q2.5"]`; `r fixef(mExtvaliPE)["age", "Q97.5"]`]), data collection mode being $\beta$ =`r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Q2.5"]`; `r fixef(mExtvaliPE)["datacollectionremoteMunsupervised", "Q97.5"]`]), and study version $\beta$ =`r fixef(mExtvaliPE)["studyversionbox", "Estimate"]` (95% CI [`r fixef(mExtvaliPE)["studyversionbox", "Q2.5"]`; `r fixef(mExtvaliPE)["studyversionbox", "Q97.5"]`]). Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze cue understanding. The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to understand the agent's gaze cue. The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the better performance in the task.

@@

```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
knitr::include_graphics("../figures/extvali_results.png")
```
